---
title: "wineclassify"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wineclassify}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document contains examples and description explaining how `wineclassify` package can be used to help the users to build a KNN classification model.

In general, the `wineclassify` package perform the following tasks to make classification analysis easier:
* Read the csv dataset from the website and turn it into a data frame
* Create a histogram and a confusion matrix with the heat map for the exploratory data analysis
* Build KNN model with the most accurate K value and return its performance with a confusion matrix

## Functions
The package includes the following functions, which can be divided into three parts:
* 1. Data loading: `data_load()` 
* 2. Visualization: `hist_plot()`, `corr_plot()`
* 3. Model building and evaluating: `model_build()`, `model_results()`

## example
To explain how the package works, we use the white wine data set stored in the repository [Github](https://raw.githubusercontent.com/kashish1928/white_wine_dataset/main/winequality-white.csv) to perform the following tasks.

### Initialization
```{r setup}
library(wineclassify)
```

### 1. Data loading
#### `data_load()`: Read the data set
The function `data_load()` can help the user download the csv data set from the website and turn it into a data frame.
```{r load}
library(wineclassify)
## basic example code
d <- data_load("https://raw.githubusercontent.com/kashish1928/white_wine_dataset/main/winequality-white.csv", ";")
d
```

### 2. Visualization
#### hist_plot()
The function `hist_plot()` plots a histogram given the data that shows the count of each category.
```{r histogram, warning=FALSE}
library(wineclassify)
hist_plot(d, "quality")
```

#### corr_plot()
The function `corr_plot()` plots a correlation matrix with heatmap from the variable pairs in the given data.
```{r}
library(wineclassify)
## basic example code
corr_plot(mtcars)
```

### 3. Model building and evaluating
#### model_build()
The function `model_build()` builds the KNN model using the most accurate K value.
```{r}
library(wineclassify)
model_build(iris, recipes::recipe(Species ~., data = iris), "Species")
```

#### model_results()
The function `model_results()` creates the confusion matrix of the fitted KNN model to assess performance.
```{r}
library(wineclassify)
split <- rsample::initial_split(iris, prop = 0.75, strata = Species)
ex_test <- rsample::testing(split)
ex_train <- rsample::training(split)
ex_recipe <- recipes::recipe(Species ~., data = ex_train)
ex_model <- model_build(ex_train, ex_recipe, "Species")
model_results(ex_test, ex_model, "Species")
```
